Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data

### 2011-05-05 ltx/data_paper/DataPaper.tex
minor edits

meaning \eqref{eq:SecondDerivativexi} is negative and $\hat{\xi}$ represents a maximum. Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of  rank $n_{\theta}$ \cite{Golub1996}. The matrix $\boldsymbol\Psi(\mathbf r')$ defined by \eqref{eq:DefPsi} is of rank $n_{\theta}$ as each row of the matrix is the set of equally spaced Gaussian basis functions with equal widths, consequently each row can be considered as a Riesz basis function for the subspaces they generate \cite{Ferrari2004}. (note that multiplying by $\mathbf \Gamma^{-1}$ doesnt change the rank). However, $q(\mathbf x_t)$ defined in \eqref{eq:QmatrixForSigmapoints} cannot be computed analytically as the inner product of a Gaussian and a sigmoid cannot be solved analytically making it difficult to calculate the rank of $q(\mathbf x_t)$ . Therefore, we recommend to check the rank of $q(\mathbf x_t)$ at each iteration.

>>>>

meaning \eqref{eq:SecondDerivativexi} is negative and $\hat{\xi}$ represents a maximum. Equation \eqref{eq:SecondDerivativetheta} is negative where $\boldsymbol\Xi_4$ is positive definite requiring $\mathbf q(\mathbf x_t)$ to be of  rank $n_{\theta}$ \cite{Golub1996}. The matrix $\boldsymbol\Psi(\mathbf r')$ defined by \eqref{eq:DefPsi} is of rank $n_{\theta}$ as each row of the matrix is a set of equally spaced Gaussian basis functions with equal widths, consequently each row can be considered as a Riesz basis function for the subspaces they generate \cite{Ferrari2004}. (note that multiplying by $\mathbf \Gamma^{-1}$ doesn't change the rank). However, $q(\mathbf x_t)$ defined in \eqref{eq:QmatrixForSigmapoints} cannot be computed analytically as the inner product of a Gaussian and a sigmoid cannot be solved analytically, making it difficult to calculate the rank of $q(\mathbf x_t)$ . Therefore, we recommend to check the rank of $q(\mathbf x_t)$ at each iteration of the E-step.
